A Tidy Framework and Infrastructure to Systematically Assemble Spatio-temporal Indexes from Multivariate Data

### 2023-08-08 tidyindex.tex
small tweaks on pipeline step details

\thanks{CONTACT: H. Sherry
Zhang. Email: \href{mailto:huize.zhang@monash.edu}{\nolinkurl{huize.zhang@monash.edu}}. }
\begin{document}
\captionsetup{labelsep=space}
\maketitle
\textsuperscript{1} Department of Econometrics and Business
Statistics, Monash University, Melbourne,
Victoria, Australia\\ \textsuperscript{2} Institute of
Statistics, University of Natural Resources and Life
Sciences, Vienna, Austria\\ \textsuperscript{3} Department of
Mathematical Sciences, BNU-HKBU United International College, Zhuhai,
Guangdong, China
\begin{abstract}
\begin{itemize}
\tightlist
\item
  indexes, useful, quantify severity, early monitoring,
\item
  A huge number of indexes have been proposed by domain experts,
  however, a large majority of them are not being adopted, reused, and
  compared in research or in practice.
\item
  One of the reasons for this is the plenty of indexes are quite complex
  and there is no obvious easy-to-use implementation to apply them to
  user's data.
\item
  The paper describes a general pipeline framework to construct indexes
  from spatio-temporal data,
\item
  This allows all the indexes to be constructed through a uniform data
  pipeline and different indexes to vary on the details of each step in
  the data pipeline and their orders.
\item
  The pipeline proposed aim to smooth the workflow of index construction
  through breaking down the complicated steps proposed by various
  indexes into small building blocks shared by most of the indexes.
\item
  The framework will be demonstrated with drought indexes as examples,
  but appliable in general to environmental indexes constructed from
  multivariate spatio-temporal data
\end{itemize}
\end{abstract}
\begin{keywords}
\def\sep{;\ }
indexes\sep data pipeline\sep 
software design
\end{keywords}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, interior hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, enhanced, sharp corners, frame hidden]}{\end{tcolorbox}}\fi

@@

\hypertarget{temporal-processing}{%
\subsubsection{Temporal processing}\label{temporal-processing}}

\textbf{Input: } multivariate data with temporal coordinates

\textbf{Output: } multivariate data with aggregated temporal axis

@@

\begin{equation}
x(\mathbf{s};\mathbf{t}^\prime)  f_{\mathcal{\psi}}(x(\mathbf{s};\mathbf{t})),
\end{equation}

@@

\hypertarget{spatial-processing}{%
\subsubsection{Spatial processing}\label{spatial-processing}}

@@

\hypertarget{variable-transformation}{%
\subsubsection{Variable transformation}\label{variable-transformation}}

@@

\hypertarget{scaling}{%
\subsubsection{Scaling}\label{scaling}}

@@

\hypertarget{dimension-reduction}{%
\subsubsection{Dimension reduction}\label{dimension-reduction}}

@@

\hypertarget{distribution-fit}{%
\subsubsection{Distribution fit}\label{distribution-fit}}

@@

\hypertarget{normalising}{%
\subsubsection{Normalising}\label{normalising}}

@@

\hypertarget{benchmarking}{%
\subsubsection{Benchmarking}\label{benchmarking}}

@@

\hypertarget{simplification}{%
\subsubsection{Simplification}\label{simplification}}

>>>>

\thanks{CONTACT: H. Sherry
Zhang. Email: \href{mailto:huize.zhang@monash.edu}{\nolinkurl{huize.zhang@monash.edu}}. }
\begin{document}
\captionsetup{labelsep=space}
\maketitle
\textsuperscript{1} Department of Econometrics and Business
Statistics, Monash University, Melbourne,
Victoria, Australia\\ \textsuperscript{2} Institute of
Statistics, University of Natural Resources and Life
Sciences, Vienna, Austria\\ \textsuperscript{3} Department of
Mathematical Sciences, BNU-HKBU United International College, Zhuhai,
Guangdong, China
\begin{abstract}
\begin{itemize}
\tightlist
\item
  indexes, useful, quantify severity, early monitoring,
\item
  A huge number of indexes have been proposed by domain experts,
  however, a large majority of them are not being adopted, reused, and
  compared in research or in practice.
\item
  One of the reasons for this is the plenty of indexes are quite complex
  and there is no obvious easy-to-use implementation to apply them to
  user's data.
\item
  The paper describes a general pipeline framework to construct indexes
  from spatio-temporal data,
\item
  This allows all the indexes to be constructed through a uniform data
  pipeline and different indexes to vary on the details of each step in
  the data pipeline and their orders.
\item
  The pipeline proposed aim to smooth the workflow of index construction
  through breaking down the complicated steps proposed by various
  indexes into small building blocks shared by most of the indexes.
\item
  The framework will be demonstrated with drought indexes as examples,
  but appliable in general to environmental indexes constructed from
  multivariate spatio-temporal data
\end{itemize}
\end{abstract}
\begin{keywords}
\def\sep{;\ }
indexes\sep data pipeline\sep 
software design
\end{keywords}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, interior hidden, boxrule=0pt, enhanced, breakable, frame hidden, sharp corners]}{\end{tcolorbox}}\fi

@@

\hypertarget{temporal-processing}{%
\subsection{Temporal processing}\label{temporal-processing}}

\textbf{Input: } \(x(\mathbf{s};\mathbf{t})\): multivariate data with
temporal coordinates

\textbf{Output: } \(x(\mathbf{s};\mathbf{t}^\prime)\): multivariate data
with aggregated temporal axis

@@

\begin{equation}
x(\mathbf{s};\mathbf{t}^\prime) = f_{\mathcal{\psi}}(x(\mathbf{s};\mathbf{t})),
\end{equation}

@@

\hypertarget{spatial-processing}{%
\subsection{Spatial processing}\label{spatial-processing}}

@@

\hypertarget{variable-transformation}{%
\subsection{Variable transformation}\label{variable-transformation}}

@@

\hypertarget{scaling}{%
\subsection{Scaling}\label{scaling}}

@@

\hypertarget{dimension-reduction}{%
\subsection{Dimension reduction}\label{dimension-reduction}}

@@

\hypertarget{distribution-fit}{%
\subsection{Distribution fit}\label{distribution-fit}}

@@

\hypertarget{normalising}{%
\subsection{Normalising}\label{normalising}}

@@

\hypertarget{benchmarking}{%
\subsection{Benchmarking}\label{benchmarking}}

@@

\hypertarget{simplification}{%
\subsection{Simplification}\label{simplification}}
